\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-01-16 tex/discussion.tex
minor edit

%The fact that such a relationship exists has the potential to unify our understanding of biological networks.
In order to further this work from a theoretical perspective, it will be necessary to deepen our understanding of the relationship between dynamical robustness and the underlying network topology.
%One approach is to attempt to compute robustness for systems of larger size. Using existing methods, this would require large-scale Monte Carlo simulations. However,
It may be possible to prove a bound on the robustness of individual SCCs, which could provide more definite knowledge and circumvent the need for expensive simulations. The conservation of robustness with respect to nontrivial symmetries including the interchange of SCCs and permutation within SCCs suggests the existence of an evolutionary neutral space. A deeper mathematical characterization of the full symmetry groupoid of dynamical robustness may thus help to characterize this potential evolutionary constraint \cite{Golubitsky2006}.

>>>>

%The fact that such a relationship exists has the potential to unify our understanding of biological networks.
In order to further this work from a theoretical perspective, it will be necessary to deepen our understanding of the relationship between dynamical robustness and the underlying network topology.
%One approach is to attempt to compute robustness for systems of larger size. Using existing methods, this would require large-scale Monte Carlo simulations. However,
It may be possible to prove bounds on the robustness of individual SCCs, which could provide more precise knowledge about the relative robustness of different network architectures. The conservation of robustness with respect to nontrivial symmetries including the interchange of SCCs and permutation within SCCs suggests the existence of an evolutionary neutral space. A deeper mathematical characterization of the full symmetry groupoid of dynamical robustness may thus help to characterize this potential evolutionary constraint \cite{Golubitsky2006}.
